Probabilistic Catalogs for Crowded Stellar Fields

### 2012-11-20 paper/ms.tex
Working on conclusions

In this paper we have developed and demonstrated a fully Bayesian approach to
making catalogs from astronomical images in the case where the image contains
only stars (or other point sources).

We note that there are many limitations to the model presented in this paper.
One such limitation is that we have not considered multi-epoch or multi-band
imaging. In the former case, stellar motions may be relevant \citep{lang}, and
in the latter, variations in the spectral energy distributions of stars will
need to be considered.

@@

{\bf Needs more words}

>>>>

In this paper we have developed and demonstrated a fully Bayesian approach to
making catalogs from astronomical images in the case where the image contains
only stars (or other point sources). The key idea is that instead of computing
a single catalog, the method creates a posterior probability distribution on
the space of possible catalogs that represents our state of knowledge about
the presence and properties of objects in the image. When this is done, the
uncertainties in the imaging are accurately propagated through to scientific
conclusions, for example about the luminosity function of the stars.
This approach was contrasted with a standard method of running \sex~and then
fitting a luminosity function to the fluxes in the catalog. This latter approach
was shown to produce incorrect inferences about the luminosity function.

We note that there are many limitations to the model presented in this paper.
In principle, our model should be a model of the physical state of the universe,
and not a simple model where the only stellar properties are a $2-D$ position and
a flux. Another limitation is that we have not considered multi-epoch or multi-band
imaging. In the former case, PSF variations and stellar motions may be relevant
\citep{lang}, and in the latter, a model for the spectral energy distributions
of the stars will need to be considered.

@@
